Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
COntestando a otro comentario de revisor y cambiando el texto para ello

The MUSES system overview is presented in Figure
\ref{fig:system_overview}. As it can be seen, in this system, the user
interacts with the devices, own or corporate, through the MUSES
graphical interface inside his or her own context (situation,
connection, status).
% This has been criticized by the reviewer and has to be changed - JJ

>>>>

The MUSES system overview is presented in Figure
\ref{fig:system_overview}. As it can be seen, in this system the user
interacts with the devices, being self-owned or corporate-owned. MUSES is running as a background process, and monitoring those interactions along with the context of the environment. Context was defined by Abowd et
al. \cite{abowd1999towards} as ``any information that can be used to
characterize the situation of an entity''. And the entity itself is defined as ``a person, place, or object that is considered relevant to the
interaction between a user and an application, including the user and applications
themselves''.
% This has been criticized by the reviewer and has to be changed - JJ
